Meta-analytic approaches and effect sizes to account for 'nuisance heterogenity' in comparative physiology

### 2021-07-21 MS/ms.Rmd
Updated document

```{r, figsurv, fig.wid = 16.833333, fig.height=6.611111,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use. (B) How many meta-analyses where ‘nuisance heterogenity’ have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity. (C) Frequency of analytical approaches used to analyse effect measures. Note that only ‘Weighted Regression’, ‘Random Effects Models’, ‘Multilevel Metaregression Models’ and ‘Multilevel Meta-analysis Models’ are weighted models. The results of this survey were drawn from 62 studies in comparative physiology."}
p1 = dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type)  %>% 
  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
                 Means = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
  mutate(effect = fct_relevel(effect, c("Other", "Zr", "lnRR", "SMD", "lnCVR", "Slope", "Means"))) %>% 
  ggplot() + tm + 
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,0.35)) +
  labs(x = "Effect Size",
       y = "Frequency") +
  coord_flip()

p2 = dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
  ggplot() + tm +
  geom_bar(aes(x = cont_moderator_variable,
               fill = cont_moderator_variable_modelled,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
  scale_fill_viridis_d() +
  theme(legend.position = c(0.45, 0.8)) + 
  labs(x = "Nuisance Heterogeneity?",
       y = "Frequency",
       fill = "Modeled Nuisance\nHeterogeneity?")

>>>>

```{r, figsurv, fig.wid = 16.833333, fig.height=5,fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their relative frequency of use. (B) How many meta-analyses where ‘nuisance heterogenity’ have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity. (C) Frequency of analytical approaches used to analyse effect measures. Note that only ‘Weighted Regression’, ‘Random Effects Models’, ‘Multilevel Metaregression Models’ and ‘Multilevel Meta-analysis Models’ are weighted models. The results of this survey were drawn from 62 studies in comparative physiology."}
p1 = dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type)  %>% 
  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
                 Means = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
  mutate(effect = fct_relevel(effect, c("Other", "Zr", "lnRR", "SMD", "lnCVR", "Slope", "Means"))) %>% 
  ggplot() + tm + 
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,0.35)) +
  labs(x = "Effect Size",
       y = "Frequency") +
  coord_flip()

p2 = dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
  ggplot() + tm +
  geom_bar(aes(x = cont_moderator_variable,
               fill = cont_moderator_variable_modelled,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
  scale_fill_viridis_d() +
  theme(legend.position = c(0.45, 0.8),
        legend.background=element_blank()) + 
  labs(x = "Nuisance Heterogeneity?",
       y = "Frequency",
       fill = "Modeled Nuisance\nHeterogeneity?")
